An overview of the oolong package.

### 2020-07-01 overview_gh.Rmd
Add BTM topic intrusion test
Add keyATM support, fix #17

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.

@@

```{r btm2}
oolong_test <- create_oolong(abstracts_btm, abstracts$text)
oolong_test
```

>>>>

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM` and Keyword Assisted Topic Models from `keyATM`.

@@

```{r btm2, error = TRUE}
oolong_test <- create_oolong(abstracts_btm, abstracts$text)
oolong_test
```
